Timeliness of security updates for Android

### 2015-03-23 avostats.tex
Updated avostats with better display of uncertainties
Update stats to include apdated avoTabAndVulns

\newcommand{\avoNumSubmitters}{7}
\newcommand{\avoTotalExternalLines}{25 Million}
\newcommand{\avoNumExternalProjects}{176}
\newcommand{\avoNumBigExternalLinesOfCode}{25 Million}
\newcommand{\avoBigExternalLinesOfCodePerc}{99.7\%}
\newcommand{\avoNumVulnerabilities}{31}
\newcommand{\avoNumVulnAllAndroid}{15}
\newcommand{\avoNumVulnSpecific}{16}
\newcommand{\avoStartDate}{2013-08-28}
\newcommand{\avoEndDate}{2014-10-17}
\newcommand{\avoFirstDataDate}{2010-07-13}
\newcommand{\avoLastDataDate}{2014-07-29}
\newcommand{\avoVulnsPerYearNominal}{7.66}
\newcommand{\avoVulnsPerYear}{$7.66 \pm 1.38$}
\newcommand{\avoVulnsPerYearAllAndroidNominal}{3.71}
\newcommand{\avoVulnsPerYearAllAndroid}{$3.71 \pm 0.957$}
\newcommand{\avoTabAndVulns}{\begin{table} \centering \small \begin{tabular}{l|l|c} Vulnerability & How known & Date \\ \hline KillingInTheNameOf & Fixed on & 2010-07-13 \\ exploid udev & Discovered on & 2010-07-15 \\ levitator & Discovered on & 2011-03-10 \\ Gingerbreak & Fixed on & 2011-04-18 \\ zergRush & Discovered on & 2011-10-06 \\ APK duplicate file & Discovered on & 2013-02-18 \\ APK unchecked name & Discovered on & 2013-06-30 \\ APK unsigned shorts & Fixed on & 2013-07-03 \\ vold asec & Fixed on & 2014-01-27 \\ Fake ID & Fixed on & 2014-04-17 \\ TowelRoot & Discovered on & 2014-05-03 \\\end{tabular} \caption{Critical vulnerabilities in Android} \label{tab:andvulns} \end{table}}
\newcommand{\avoNumBigExternalProjects}{40}
\newcommand{\avoNumAnalysedExternalProjects}{28}
\newcommand{\avoNumAnalysedExternalLinesOfCode}{6 Million}
\newcommand{\avoAnalysedExternalLinesOfCodePerc}{24.9\%}
\newcommand{\avoBigExternalMedianVersions}{1.5}
\newcommand{\avoBigExternalMeanVersionsNominal}{2.07}
\newcommand{\avoBigExternalMeanVersions}{$2.07 \pm 1.44$}
\newcommand{\avoBigExternalTotalVersions}{58}

>>>>

\newcommand{\avoNumSubmitters}{7}
\newcommand{\avoTotalExternalLines}{25 Million}
\newcommand{\avoNumExternalProjects}{176}
\newcommand{\avoNumBigExternalLinesOfCode}{25 Million}
\newcommand{\avoBigExternalLinesOfCodePerc}{99.7\%}
\newcommand{\avoNumVulnerabilities}{31}
\newcommand{\avoNumVulnAllAndroid}{15}
\newcommand{\avoNumVulnSpecific}{16}
\newcommand{\avoStartDate}{2013-08-28}
\newcommand{\avoEndDate}{2014-10-17}
\newcommand{\avoFirstDataDate}{2010-07-13}
\newcommand{\avoLastDataDate}{2014-07-29}
\newcommand{\avoVulnsPerYearNominal}{7.66}
\newcommand{\avoVulnsPerYear}{$7.66 \pm 1.38$}
\newcommand{\avoVulnsPerYearAllAndroidNominal}{3.71}
\newcommand{\avoVulnsPerYearAllAndroid}{$3.71 \pm 0.95$}
\newcommand{\avoTabAndVulns}{\begin{table} \centering \small \begin{tabular}{l|l|c|c} Vulnerability & How known & Date & Categories\\ \hline KillingInTheNameOf & Fixed on & 2010-07-13 & system, kernel\\ exploid udev & Discovered on & 2010-07-15 & kernel\\ levitator & Discovered on & 2011-03-10 & kernel\\ Gingerbreak & Fixed on & 2011-04-18 & system\\ zergRush & Discovered on & 2011-10-06 & system\\ APK duplicate file & Discovered on & 2013-02-18 & signature\\ APK unchecked name & Discovered on & 2013-06-30 & signature\\ APK unsigned shorts & Fixed on & 2013-07-03 & signature\\ vold asec & Fixed on & 2014-01-27 & system\\ Fake ID & Fixed on & 2014-04-17 & signature\\ TowelRoot & Discovered on & 2014-05-03 & kernel\\\end{tabular} \caption{Critical vulnerabilities in Android} \label{tab:andvulns} \end{table}}
\newcommand{\avoNumBigExternalProjects}{40}
\newcommand{\avoNumAnalysedExternalProjects}{28}
\newcommand{\avoNumAnalysedExternalLinesOfCode}{6 Million}
\newcommand{\avoAnalysedExternalLinesOfCodePerc}{24.9\%}
\newcommand{\avoBigExternalMedianVersions}{1.5}
\newcommand{\avoBigExternalMeanVersionsNominal}{2.07}
\newcommand{\avoBigExternalMeanVersions}{$2.07 \pm 1.44$}
\newcommand{\avoBigExternalTotalVersions}{58}

### 2015-03-23 dastats.tex
Strip out security updates and android ecosystem stuff from esorics paper and put in a ccs paper and make the esorics paper meet the page limit
Squash figures up together to save space - bad idea
Update stats to include apdated avoTabAndVulns

\newcommand{\daNumManufacturers}{292}

@@

\newcommand{\daNumModels}{2\,620}

@@

\newcommand{\daMeanOutstandingVulnerabilities}{0.582}
\newcommand{\daUpdatedness}{$0.0521 \pm 0.0002$}

@@

\newcommand{\daNumOSVersionUpdates}{3\,720}
\newcommand{\daNumFullOnlyVersionUpdates}{663}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline LG & $0.18 \pm 0.00$ & $0.32 \pm 0.00$ & 0.67 & $3.70 \pm 0.01$ \\  Motorola & $0.16 \pm 0.00$ & $0.13 \pm 0.00$ & 0.78 & $2.93 \pm 0.01$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & 0.67 & $2.67 \pm 0.00$ \\  Sony & $0.12 \pm 0.00$ & $0.19 \pm 0.00$ & 1.11 & $2.55 \pm 0.01$ \\  HTC & $0.13 \pm 0.00$ & $0.08 \pm 0.00$ & 0.94 & $2.48 \pm 0.00$ \\  asus & $0.18 \pm 0.00$ & $0.52 \pm 0.01$ & 6.01 & $2.30 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.04 \pm 0.00$ & 1.11 & $1.87 \pm 0.00$ \\  Symphony & $0.00 \pm 0.00$ & $0.07 \pm 0.00$ & 4.98 & $0.25 \pm 0.00$ \\  walton & $0.00 \pm 0.00$ & $0.07 \pm 0.00$ & 5.97 & $0.21 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table}}
\newcommand{\daTabSecScoresmodel}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.51 \pm 0.00$ & $0.53 \pm 0.01$ & 1.53 & $4.71 \pm 0.03$ \\  Nexus 4 & $0.29 \pm 0.00$ & $0.82 \pm 0.01$ & 6.06 & $3.63 \pm 0.04$ \\  Nexus 7 & $0.24 \pm 0.00$ & $0.74 \pm 0.01$ & 5.92 & $3.19 \pm 0.04$ \\  other & $0.09 \pm 0.00$ & $0.14 \pm 0.00$ & 0.58 & $2.92 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & 0.39 & $2.91 \pm 0.02$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & 1.59 & $2.43 \pm 0.02$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & 1.23 & $2.28 \pm 0.01$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & 1.00 & $1.75 \pm 0.01$ \\  GT-N7000 & $0.24 \pm 0.00$ & $0.00 \pm 0.00$ & 2.53 & $1.42 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & 1.73 & $0.94 \pm 0.02$ \\  GT-I9300 & $0.14 \pm 0.00$ & $0.01 \pm 0.00$ & 6.28 & $0.59 \pm 0.01$ \\  GT-I9505 & $0.00 \pm 0.00$ & $0.14 \pm 0.00$ & 6.86 & $0.44 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & 3.05 & $0.27 \pm 0.02$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & 6.90 & $0.26 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & 11.00 & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table}}
\newcommand{\daTabSecScoressummary}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline nexus & $0.40 \pm 0.00$ & $0.49 \pm 0.00$ & 0.62 & $5.14 \pm 0.01$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & 0.58 & $2.61 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table}}
\newcommand{\daUpdatednessPerc}{$5.21 \pm 0.02\%$}
\newcommand{\daNumOSDevices}{20\,000}

@@

\newcommand{\daSecScoreBestmanufacturerScore}{$3.7 \pm 0.0$}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.214 \pm 0.006$}

@@

\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0281$}

@@

\newcommand{\daPercUpdatesDowngrades}{$3.52 \pm 0.29\%$}

@@

\newcommand{\daEndDate}{2015-03-04}

@@

\newcommand{\daTabSecScoresoperator}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.25 \pm 0.00$ & $0.12 \pm 0.00$ & 0.37 & $3.82 \pm 0.01$ \\  T-Mobile & $0.20 \pm 0.00$ & $0.18 \pm 0.00$ & 0.48 & $3.62 \pm 0.01$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & 0.39 & $3.52 \pm 0.02$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & 0.44 & $3.39 \pm 0.01$ \\  3 & $0.16 \pm 0.00$ & $0.09 \pm 0.00$ & 0.49 & $3.20 \pm 0.01$ \\  Vodafone uk & $0.14 \pm 0.00$ & $0.13 \pm 0.00$ & 0.50 & $3.20 \pm 0.01$ \\  AT\&T & $0.12 \pm 0.00$ & $0.08 \pm 0.00$ & 0.43 & $3.07 \pm 0.01$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & 0.82 & $2.82 \pm 0.01$ \\  unknown & $0.10 \pm 0.00$ & $0.21 \pm 0.00$ & 0.95 & $2.72 \pm 0.01$ \\  n Telenor & $0.03 \pm 0.00$ & $0.11 \pm 0.00$ & 1.43 & $1.59 \pm 0.01$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & 1.87 & $1.08 \pm 0.01$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 2.02 & $0.85 \pm 0.00$ \\  Robi & $0.00 \pm 0.00$ & $0.06 \pm 0.00$ & 2.09 & $0.84 \pm 0.01$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 2.71 & $0.48 \pm 0.00$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table}}

@@

\newcommand{\daSecScoreWorstoperatorScore}{$0.485 \pm 0.004$}

@@

\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{122}

@@

\newcommand{\daSecScoreBestoperatorNumFullVersions}{92}

@@

\newcommand{\daOSCurveFitParamFirst}{87.5}
\newcommand{\daOSCurveFitParamSecond}{\num{0.00301}}

@@

\newcommand{\daAPICurveFitParamSecond}{\num{0.00299}}
\newcommand{\daAPICurveFitRMSE}{0.115}

@@

\newcommand{\daOSCurveHalfDeployed}{$318 \pm 87$}
\newcommand{\daOSCurveFullDeployed}{$1\,080 \pm 247\,000$}

@@

\newcommand{\daAPICurveHalfDeployed}{$337 \pm 87$}
\newcommand{\daAPICurveFullDeployed}{$1\,110 \pm 248\,000$}

@@

\newcommand{\daPercBigUpgrades}{$18.7 \pm 0.7\%$}

@@

\newcommand{\daOSMonthsOfData}{44}

@@

\newcommand{\daUpdatednessNominal}{0.0521}
\newcommand{\daUpdatednessPercNominal}{5.21\%}

@@

\newcommand{\daOSCurveHalfDeployedNominal}{318}
\newcommand{\daOSCurveFullDeployedNominal}{1\,080}
\newcommand{\daAPICurveHalfDeployedNominal}{337}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.485}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.7}
\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.214}
\newcommand{\daUpdatesPerMonthPerVersion}{$3.04 \pm 0.05$}
\newcommand{\daNumUpdateFullOnly}{660}

@@

\newcommand{\daUpdatesPerMonthPerVersionNominal}{3.04}
\newcommand{\daPercBigUpgradesNominal}{18.7\%}
\newcommand{\daPercUpdatesDowngradesNominal}{3.52\%}

@@

\newcommand{\daOSCurveHalfDeployedYearsNominal}{0.871}
\newcommand{\daOSCurveHalfDeployedYears}{$0.871 \pm 0.24$}
\newcommand{\daOSCurveFullDeployedYearsNominal}{2.97}
\newcommand{\daOSCurveFullDeployedYears}{$2.97 \pm 67$}
\newcommand{\daAPICurveHalfDeployedYearsNominal}{0.923}
\newcommand{\daAPICurveHalfDeployedYears}{$0.923 \pm 0.238$}
\newcommand{\daAPICurveFullDeployedYearsNominal}{3.03}
\newcommand{\daAPICurveFullDeployedYears}{$3.03 \pm 67$}

@@

>>>>

\newcommand{\daNumManufacturers}{293}

@@

\newcommand{\daNumModels}{2\,640}

@@

\newcommand{\daMeanOutstandingVulnerabilities}{0.578}
\newcommand{\daUpdatedness}{$0.0522 \pm 0.0002$}

@@

\newcommand{\daNumOSVersionUpdates}{3\,730}
\newcommand{\daNumFullOnlyVersionUpdates}{664}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline LG & $0.18 \pm 0.00$ & $0.32 \pm 0.00$ & 0.67 & $3.71 \pm 0.01$ \\  Motorola & $0.16 \pm 0.00$ & $0.13 \pm 0.00$ & 0.78 & $2.93 \pm 0.01$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & 0.66 & $2.68 \pm 0.00$ \\  Sony & $0.12 \pm 0.00$ & $0.19 \pm 0.00$ & 1.11 & $2.55 \pm 0.01$ \\  HTC & $0.13 \pm 0.00$ & $0.08 \pm 0.00$ & 0.94 & $2.48 \pm 0.00$ \\  asus & $0.18 \pm 0.00$ & $0.52 \pm 0.01$ & 6.01 & $2.30 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.04 \pm 0.00$ & 1.11 & $1.87 \pm 0.00$ \\  Symphony & $0.00 \pm 0.00$ & $0.07 \pm 0.00$ & 5.00 & $0.25 \pm 0.00$ \\  walton & $0.00 \pm 0.00$ & $0.07 \pm 0.00$ & 6.00 & $0.24 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table}}
\newcommand{\daTabSecScoresmodel}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.51 \pm 0.00$ & $0.53 \pm 0.01$ & 1.53 & $4.71 \pm 0.03$ \\  Nexus 4 & $0.29 \pm 0.00$ & $0.82 \pm 0.01$ & 6.06 & $3.64 \pm 0.04$ \\  Nexus 7 & $0.24 \pm 0.00$ & $0.74 \pm 0.01$ & 5.92 & $3.19 \pm 0.04$ \\  other & $0.09 \pm 0.00$ & $0.14 \pm 0.00$ & 0.58 & $2.93 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & 0.39 & $2.91 \pm 0.02$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & 1.59 & $2.43 \pm 0.02$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & 1.23 & $2.28 \pm 0.01$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & 1.00 & $1.75 \pm 0.01$ \\  GT-N7000 & $0.24 \pm 0.00$ & $0.00 \pm 0.00$ & 2.53 & $1.42 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & 1.73 & $0.94 \pm 0.02$ \\  GT-I9300 & $0.14 \pm 0.00$ & $0.01 \pm 0.00$ & 6.28 & $0.59 \pm 0.01$ \\  GT-I9505 & $0.00 \pm 0.00$ & $0.14 \pm 0.00$ & 6.87 & $0.44 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & 3.05 & $0.27 \pm 0.02$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & 6.90 & $0.26 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & 11.00 & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table}}
\newcommand{\daTabSecScoressummary}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline nexus & $0.40 \pm 0.00$ & $0.49 \pm 0.00$ & 0.62 & $5.14 \pm 0.01$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & 0.58 & $2.62 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table}}
\newcommand{\daUpdatednessPerc}{$5.22 \pm 0.02\%$}
\newcommand{\daNumOSDevices}{20\,100}

@@

\newcommand{\daSecScoreBestmanufacturerScore}{$3.71 \pm 0.01$}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.24 \pm 0.00$}

@@

\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.028$}

@@

\newcommand{\daPercUpdatesDowngrades}{$3.51 \pm 0.29\%$}

@@

\newcommand{\daEndDate}{2015-03-13}

@@

\newcommand{\daTabSecScoresoperator}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.25 \pm 0.00$ & $0.12 \pm 0.00$ & 0.37 & $3.82 \pm 0.01$ \\  T-Mobile & $0.20 \pm 0.00$ & $0.18 \pm 0.00$ & 0.48 & $3.62 \pm 0.01$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & 0.39 & $3.52 \pm 0.02$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & 0.44 & $3.39 \pm 0.01$ \\  3 & $0.16 \pm 0.00$ & $0.09 \pm 0.00$ & 0.49 & $3.21 \pm 0.01$ \\  Vodafone uk & $0.14 \pm 0.00$ & $0.13 \pm 0.00$ & 0.50 & $3.20 \pm 0.01$ \\  AT\&T & $0.12 \pm 0.00$ & $0.08 \pm 0.00$ & 0.43 & $3.07 \pm 0.01$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & 0.82 & $2.82 \pm 0.01$ \\  unknown & $0.10 \pm 0.00$ & $0.21 \pm 0.00$ & 0.95 & $2.72 \pm 0.01$ \\  n Telenor & $0.03 \pm 0.00$ & $0.11 \pm 0.00$ & 1.43 & $1.59 \pm 0.01$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & 1.86 & $1.09 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.07 \pm 0.00$ & 2.10 & $0.86 \pm 0.01$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 2.04 & $0.84 \pm 0.00$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 2.72 & $0.48 \pm 0.00$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table}}

@@

\newcommand{\daSecScoreWorstoperatorScore}{$0.484 \pm 0.004$}

@@

\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{123}

@@

\newcommand{\daSecScoreBestoperatorNumFullVersions}{93}

@@

\newcommand{\daOSCurveFitParamFirst}{87.3}
\newcommand{\daOSCurveFitParamSecond}{\num{0.00299}}

@@

\newcommand{\daAPICurveFitParamSecond}{\num{0.00298}}
\newcommand{\daAPICurveFitRMSE}{0.114}

@@

\newcommand{\daOSCurveHalfDeployed}{$319 \pm 88$}
\newcommand{\daOSCurveFullDeployed}{$1\,090 \pm 248\,000$}

@@

\newcommand{\daAPICurveHalfDeployed}{$338 \pm 87$}
\newcommand{\daAPICurveFullDeployed}{$1\,110 \pm 249\,000$}

@@

\newcommand{\daPercBigUpgrades}{$18.6 \pm 0.7\%$}

@@

\newcommand{\daOSMonthsOfData}{45}

@@

\newcommand{\daUpdatednessNominal}{0.0522}
\newcommand{\daUpdatednessPercNominal}{5.22\%}

@@

\newcommand{\daOSCurveHalfDeployedNominal}{319}
\newcommand{\daOSCurveFullDeployedNominal}{1\,090}
\newcommand{\daAPICurveHalfDeployedNominal}{338}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.484}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.71}
\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.24}
\newcommand{\daUpdatesPerMonthPerVersion}{$2.98 \pm 0.05$}
\newcommand{\daNumUpdateFullOnly}{661}

@@

\newcommand{\daUpdatesPerMonthPerVersionNominal}{2.98}
\newcommand{\daPercBigUpgradesNominal}{18.6\%}
\newcommand{\daPercUpdatesDowngradesNominal}{3.51\%}

@@

\newcommand{\daOSCurveHalfDeployedYearsNominal}{0.874}
\newcommand{\daOSCurveHalfDeployedYears}{$0.874 \pm 0.242$}
\newcommand{\daOSCurveFullDeployedYearsNominal}{2.98}
\newcommand{\daOSCurveFullDeployedYears}{$2.98 \pm 67$}
\newcommand{\daAPICurveHalfDeployedYearsNominal}{0.925}
\newcommand{\daAPICurveHalfDeployedYears}{$0.925 \pm 0.239$}
\newcommand{\daAPICurveFullDeployedYearsNominal}{3.04}
\newcommand{\daAPICurveFullDeployedYears}{$3.04 \pm 68$}

@@

\newcommand{\daUpdatednessPercTwosfNominal}{5.2\%}
\newcommand{\daUpdatednessPercTwosf}{$5.2 \pm 0.0\%$}
